comparing_scenario

### 2021-02-20 comparing_scenario.Rmd
Change the code as the flag changed.
Change the method to rlm.

```{r}
load("wages_hs2020.rda")
load("wages_hs2020_weighted.rda")
wages_old <- brolgar::wages %>%
  mutate(mean_hourly_wage = exp(ln_wages))
```

@@

wages_old <- as_tsibble(x = wages_old,
                    key = id,
                    index = xp,
                    regular = FALSE)
```

@@

print("Weighted data, extreme value excluded")
get_summary(filter(wages_weighted, flag2 == "non_ext_val"))
```

>>>>

```{r}
load("wages_hs2020.rda")
load("wages_hs2020_weighted.rda")
wages_old <- brolgar::wages %>%
  mutate(mean_hourly_wage = exp(ln_wages))
load("wages_hs2020_weighted_updated2018.rda")
```

@@

wages_old <- as_tsibble(x = wages_old,
                    key = id,
                    index = xp,
                    regular = FALSE)

wages_weighted_2018 <- 
```

@@

print("Weighted data, extreme value excluded")
get_summary(filter(wages_weighted, is_extreme_val == FALSE))
```
